Old or Heavy?\\Decaying Gracefully with Age/Weight Shapes.

### 2019-03-02 papers/CADE19/paper.tex
remove comparative section
extra test in experiments

Overall, the baseline solved the most problems (13,057)
No experimental configuration improved on this figure, but some problems not solved by baseline were solved by the new configurations, and some entirely new problems were solved.
The union of all \emph{converge} and \emph{decay} configurations improved on the baseline, with 13,167 and 13,106 solved problems respectively.

Figure \ref{tab:results} shows the performance in terms of solved problems of all the configurations tested.
These data show that configurations which are more similar to the baseline (i.e. slow decay or fast convergence) achieve more similar performance, as expected.
In total, 134 problems were solved by the new configurations that were not solved by the baseline.

%\subsection{New Problems}
Two problems were solved which were marked with an ``Unknown'' status in the TPTP headers.
Only converging with frequency 50 solved \texttt{SET345-6} and only decaying with frequency 1 solved \texttt{LAT320+3}.

@@

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with other Solvers}

@@

To place these results in context, we compare the overall number of problems solved by our new strategies with the results of other solvers (using their previous CASC competition strategy). These results are from 300s and are given in Table~\ref{tab:other}.

>>>>

Overall, the baseline solved the most problems (13,057). 
No experimental configuration improved on this figure, but some problems not solved by baseline were solved by the new configurations, and some entirely new problems were solved.
The union of all \emph{converge} and \emph{decay} configurations improved on the baseline, with 13,167 and 13,106 solved problems respectively.

Figure \ref{tab:results} shows the performance in terms of solved problems of all the configurations tested.
These data show that configurations which are more similar to the baseline (i.e. slow decay or fast convergence) achieve more similar performance, as expected.
In total, 134 problems were solved by the new configurations that were not solved by the baseline. This is an impressive result - it is rare to be able to improve portfolio mode by this many new problems with a single new proof search option.

We also report the \emph{u-score} computed by giving $1/n$ points per problem solved where $n$ is the number of strategies solving a problem. This gives a measure of contribution per strategy. To consider new options for extending the portfolio mode we will consider options from largest u-score to smallest (and only those with unique solutions overall).

%\subsection{New Problems}
Finally, two problems were solved which were marked with an ``Unknown'' status in the TPTP headers.
Only converging with frequency 50 solved \texttt{SET345-6} and only decaying with frequency 1 solved \texttt{LAT320+3}.

@@

\iffalse
%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with other Solvers}

@@

To place these results in context, we compare the overall number of problems solved by our new strategies with the results of other solvers (using their previous CASC competition strategy). These results are from 300s and are given in Table~\ref{tab:other}. 
\fi
